---
title: "Exercise 2.9.1"
---

```{r include=FALSE} 
knitr::opts_chunk$set(options(scipen = 999))
knitr::opts_chunk$set(echo = FALSE)
```

> If replacement is allowed, find all:
> 
> (a) 5-permutations of a 2-set

*Please note that my solution differs from the authors' one given at the end*

```{r results='asis'}
library(gtools)
knitr::opts_chunk$set(echo = FALSE)

formatted_strings = apply(permutations(2, 5, letters[1:3], repeats.allowed = TRUE), 1, function(x) {cat("1. $\\{", paste(x, collapse=", "), "\\}$", "\n")})
discarded_result <- lapply(formatted_strings, function(x){cat(x)})
```

Authors' answer: $aaaa, aaab, aaba, abaa, baaa, aabb, abab, abba, baab, baba, bbaa, abbb, babb, bbab, bbba, bbbb;$[^1]

> (b) 2-permutations of a 3-set

```{r results='asis'}
library(gtools)
knitr::opts_chunk$set(echo = FALSE)

formatted_strings = apply(permutations(3, 2, letters[1:3], repeats.allowed = TRUE), 1, function(x) {cat("1. $\\{", paste(x, collapse=", "), "\\}$", "\n")})
discarded_result <- lapply(formatted_strings, function(x){cat(x)})
```


> (c) 5-combinations of a 2-set

*Please note that my solution differs from the authors' one given at the end*

```{r results='asis'}
library(gtools)
knitr::opts_chunk$set(echo = FALSE)

formatted_strings = apply(combinations(2, 5, letters[1:2], repeats.allowed = TRUE), 1, function(x) {cat("1. $\\{", paste(x, collapse=", "), "\\}$", "\n")})
discarded_result <- lapply(formatted_strings, function(x){cat(x)})
```

Authors' answer: $\{a, a, a, a\}, \{a, a, a, b\}, \{a, a, b, b\}, \{a, b, b, b\}, \{b, b, b, b\};$[^2]

> (d) 2-combinations of a 3-set

```{r results='asis'}
library(gtools)
knitr::opts_chunk$set(echo = FALSE)

formatted_strings = apply(combinations(3, 2, letters[1:3], repeats.allowed = TRUE), 1, function(x) {cat("1. $\\{", paste(x, collapse=", "), "\\}$", "\n")})
discarded_result <- lapply(formatted_strings, function(x){cat(x)})
```

[^1]: Clearly a typo, the authors posted 4-permutations, instead of 5-permutations, of a 2-set 
[^2]: Similarly looks like a typo, the authors posted 4-combinations, instead of 5-combinations, of a 2-set